---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# samuelr

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/samuelkordik/samuelr/graph/badge.svg)](https://app.codecov.io/gh/samuelkordik/samuelr)
<!-- badges: end -->

Welcome to my personal R package! This is a collection of useful tools and utilities I use to solve common problems I encounter. Feel free to borrow what you find beneficial.

## Installation

You can install the development version of samuelr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("samuelkordik/samuelr")
```

## Key Functions

### if_error
Function wrapper to gracefully handle errors (similar to Excel's IFERROR function):

```{r example}
#library(samuelr)
#log_or_na <- if_error(log) # Returns log() but if there's an error, just returns NA.
#log_or_na(2)
# [1] 0.6931472
#log_or_na("A")
# non-numeric argument to mathematical function
# [1] NA

```
